An application of Graph Theory to MDAO problem formulation

### 2012-10-04 intro.tex
adding XDSM

    An alternate matrix based syntax, called a Functional Dependency Table (FDT), was proposed by Michelena and Papalambros. 
    FDT represents the relationship between functions, including objectives and constraints, and specific variables that affect 
    them\cite{Michelena1997}. Similar to DSM, FDT also describes an adjacency matrix of a graph. Unlike the DSM graph, 
    however, the graph is undirected and nodes can represent analysis tools, objectives, 
    or constraints. Edges between nodes represent a dependence on the same 
    variable. Wagner and Papalambros made use of the FDT to solve a graph partitioning problem that yielded 
    more efficient optimization problem decompositions\cite{Wagner1993}. While FDT succeeds at capturing the 
    information about objectives and constraints, it neglects the data dependency captured by DSM. 
    [TODO: There is more recent research to cite here. e.g. Allison's Work.]

    [TODO: insert FDT of simple problem here]

>>>>

    An alternate matrix based syntax, called a Functional Dependency Table (FDT), was proposed by Michelena and Papalambros. 
    FDT represents the relationship between functions, including objectives and constraints, and specific variables that affect 
    them\cite{Michelena1997}. Similar to DSM, FDT also describes an adjacency matrix of a graph. Unlike the DSM graph, 
    however, the graph is undirected and nodes can represent analysis tools, objectives, 
    or constraints. Edges between nodes represent a dependence on the same 
    variable. Wagner and Papalambros made use of the FDT to solve a graph partitioning problem that yielded 
    more efficient optimization problem decompositions\cite{Wagner1993}. While FDT succeeds at capturing the 
    information about objectives and constraints, it neglects the data dependency captured by DSM. For instance, 
    although we know from the FPF in Eqn. \ref{eqn:simple_fpf} that the objective, $f$, is dependent on the 
    output of analysis $A$, you could not determine that from the FDT in Fig. \ref{fig:FDT_simple} alone.

    [TODO: There is more recent research to cite here. e.g. Allison's Work.]

    \begin{figure}
        \begin{center}
        \begin{tabular}{|c|c|c|c|c|c|c|}
            \hline
                 & $x$ & $y$ & $y^t$ & $z$ & $z^t$ & m \\ \hline
            $A$  & 1  & 1    &       &     &       &   \\ \hline
            $B$  & 1  &      &       & 1   &       &   \\ \hline
            $f$  &    &      &       &     &       & 1 \\ \hline
            $g1$ &    &      &       & 1   & 1     &   \\ \hline
            $g2$ &    & 1    & 1     &     &       &   \\
            \hline
        \end{tabular}
        \caption{Functional Dependency Table (FDT) for Eqn. \ref{eqn:simple_fpf} \label{fig:FDT_simple}}
        \end{center}
    \end{figure}
